The Multi-Stencil Language

### 2016-05-26 ARTICLES/IJPP/article/evaluation.tex
IJPP article modifications evaluation

Finally, to completely validate the performance model introduced in Section~\ref{sect:perfs}, and to understand when the hybrid parallelization becomes more interesting than the data parallelization, Figure~\ref{tth2} represents $T_{COM1}$ and $T_{COM2}+T_{task}$ of Equation~(\ref{eq:hyb}), for the best case, \ie when 8 cores are used for task parallelization, and with a \emph{close} OpenMP bind of threads onto cores. Table~\ref{fig:tth} gives time details.

>>>>

Finally, to completely validate the performance model introduced in Section~\ref{sect:perfs}, and to understand when the hybrid parallelization becomes more interesting than the data parallelization, Figure~\ref{fig:tth2} represents $T_{COM1}$ and $T_{COM2}+T_{task}$ of Equation~(\ref{eq:hyb}), for the best case, \ie when 8 cores are used for task parallelization, and with a \emph{close} OpenMP bind of threads onto cores. Table~\ref{fig:tth} gives time details.
